Thesis outline

### 2017-06-16 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Updated Paper 3

%%%% Brighter star-forming galaxies %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To see how our results of the environmental dependence of dwarf galaxies compare 
with somewhat brighter galaxies, we perform the same analysis on galaxies with 
absolute magnitudes $-17 > M_r > -20$.  The results of this analysis can be seen 
in Figs. \ref{fig:Z_bright} and \ref{fig:N_bright}.  As the dwarf galaxies have 
already shown, there is no obvious large-scale environmental dependence of the 
oxygen and nitrogen abundances of these brighter galaxies.  The results of a 
two-sample K-S test (listed in Table \ref{tab:stats}) mostly support this 
conclusion.  In the brightest magnitude bin (galaxies with $-19 > M_r > -20$), 
the K-S test returns a $p$-value of only 0.00062 for the oxygen abundances, 
indicating only a 0.062\% chance that there will be a test statistic greater 
than 0.07 if the void sample is drawn from the wall sample.  The oxygen 
abundances for void galaxies are higher than the wall galaxies by an average of 
$0.04\pm 0.017$ in this absolute magnitude bin, reinforcing the results of the 
K-S test that there is a large-scale environmental influence on the oxygen 
abundance in galaxies with magnitudes $-19 > M_r > -20$.  While the results of 
the K-S test are not as convincing for this magnitude range in the nitrogen 
abundances, there is still an average shift of $0.02\pm 0.011$ toward higher 
nitrogen abundances for void galaxies.  While only one magnitude bin shows a 
statistically significant shift between the two environments, all magnitude bins 
are shifted in the same direction.  This trend suggests that there may be a mild 
influence on the chemical evolution of galaxies due to their large-scale 
environment.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_12logOH_stacked}
    \caption[Metallicity distribution of star-forming galaxies with 
    $-17 > M_r > -20$]{Gas-phase oxygen abundances relative to hydrogen of void 
    (red solid line) and wall (black dashed line) star-forming galaxies with 
    $-17 > M_r > -18$ (top), $-18 > M_r > -19$ (middle), and $-19 > M_r > -20$ 
    (bottom).  The results of a two-sample K-S test of the two data sets in each 
    absolute magnitude range can be found in Table \ref{tab:stats}.  These 
    results are reflected visually, as there appears to be very little 
    difference between the two populations (regardless of absolute magnitude), 
    indicating that there is little large-scale environmental influence on the 
    oxygen abundance of star-forming galaxies with absolute magnitudes 
    $-17 > M_r > -20$.}
    \label{fig:Z_bright}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_12logNH_stacked}
    \caption[Nitrogen distribution of star-forming galaxies with 
    $-17 > M_r > -20$]{Abundance of nitrogen relative to hydrogen of void (red 
    solid line) and wall (black dashed line) star-forming galaxies with 
    $-17 > M_r > -18$ (top), $-18 > M_r > -19$ (middle), and $-19 > M_r > -20$ 
    (bottom).  The results of a two-sample K-S test of the two data sets in each 
    absolute magnitude range can be found in Table \ref{tab:stats}.  These 
    results are reflected visually, as there appears to be very little 
    difference between the two populations (regardless of absolute magnitude), 
    indicating that there is little large-scale environmental influence on the 
    nitrogen abundance of star-forming galaxies with absolute magnitudes 
    $-17 > M_r > -20$.}
    \label{fig:N_bright}
\end{figure}

@@

%%%% Brighter star-forming galaxies %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We perform the same analysis with the N/O ratio on somewhat brighter galaxies, 
up through $M_r > -20$; the results of this analysis can be seen in Fig. 
\ref{fig:NO_bright} and in Table \ref{tab:stats}.  The shift toward lower N/O 
ratios for the void galaxies is small for all magnitude bins.  The direction of 
the shift between environments for the N/O ratio is consistent for all absolute 
magnitude bins: void galaxies have slightly lower N/O ratios than wall galaxies.  
This is only very weak evidence of a large-scale environmental influence on the 
relative abundances of elements in galaxies, but it is worth testing for in 
larger samples.

% 17-18
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_logNO_stacked}
    \caption[N/O distribution of star-forming galaxies with $-17 > M_r > -20$]
    {Ratio of nitrogen to oxygen of void (red solid line) and wall (black dashed 
    line) star-forming galaxies with $-17 > M_r > -18$ (top), $-18 > M_r > -19$ 
    (middle), and $-19 > M_r > -20$ (bottom).  The results of a two-sample K-S 
    test of the two data sets in each absolute magnitude range can be found in 
    Table \ref{tab:stats}, in addition to other statistics of the samples.  Both 
    the histograms, CDFs, and statistics suggest a very slight difference 
    between the two populations, indicating a mild large-scale environmental 
    influence on the relative chemical abundances of star-forming galaxies with 
    absolute magnitudes $-17 > M_r > -20$.}
    \label{fig:NO_bright}
\end{figure}

@@

	\label{tab:stats}

@@

The majority of the shifts in the gas-phase abundances of oxygen, nitrogen, and 
the N/O ratio seen in galaxies fainter than $L_*$ are small and statistically 
insignificant.  However, they occur in almost the same direction across all 
magnitude bins.  This trend suggests that the gas-phase abundances may be 
influenced by the galaxies' large-scale environments.  \cite{Shields91} find no 
offset in the N/O ratio between cluster and field galaxies, despite the 
difference in O/H they observe.  Similar to us, \cite{Contini02} and 
\cite{Pilyugin02} also find a statistically insignificant shift in the N/O ratio 
of cluster galaxies, although they find that these galaxies have lower N/O 
ratios than field spiral galaxies.  Based on Fig. \ref{fig:NOratio} and the 
statistics in Table \ref{tab:stats}, we find weak evidence that void dwarf 
galaxies have a smaller N/O ratio than dwarf galaxies in denser regions.  This 
means that void dwarf galaxies may have more oxygen than wall dwarf galaxies, 
and/or void dwarf galaxies could have less nitrogen than wall dwarf galaxies.  
Here we discuss these possibilities and explore their implications for the 
large-scale environmental impact on the formation and evolution of galaxies.

@@

Table \ref{tab:stats} suggests a slight large-scale environmental dependence of 
the oxygen and nitrogen abundances (relative to hydrogen), where void galaxies 
have slightly more O/H and N/H than wall galaxies.  This small difference is 
not apparent when looking at Figs. \ref{fig:met1sig} and \ref{fig:N_1sig}.  
However, the N/O ratio amplifies this large-scale environmental effect so that a 
shift in the mean (or median) of the two populations can be seen in Fig. 
\ref{fig:NOratio}.  We hesitate to combine the results across all magnitude bins 
in an effort to improve their significance.  Instead, we look toward the future 
to analyze a larger sample of galaxies to increase the statistical significance 
of these results.

@@

Applying the results of these simulations to our dwarf galaxy sample, if the 
ratio of dark matter halo mass to stellar mass is larger in void galaxies, the 
metals ejected from a void galaxy's ISM into its circumgalactic medium are more 
likely to fall back onto the ISM than in a wall galaxy with the same stellar 
mass, since the void galaxy's virial radius and potential well are larger.  As a 
result, two dwarf galaxies with the same stellar mass in these two different 
large-scale environments can have different metallicities --- void dwarf 
galaxies would have higher metallicities than wall dwarf galaxies, matching what 
we see in Table \ref{tab:stats}.

>>>>

%%%% Brighter star-forming galaxies %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To see how our results of the environmental dependence of dwarf galaxies compare 
with somewhat brighter galaxies, we perform the same analysis on galaxies with 
absolute magnitudes $-17 > M_r > -20$.  The results of this analysis can be seen 
in Figs. \ref{fig:Z_bright} and \ref{fig:N_bright}.  As the dwarf galaxies have 
already shown, there is no obvious large-scale environmental dependence of the 
oxygen and nitrogen abundances of these brighter galaxies.  The results of a 
two-sample K-S test (listed in Table \ref{tab:stats_P2}) mostly support this 
conclusion.  In the brightest magnitude bin (galaxies with $-19 > M_r > -20$), 
the K-S test returns a $p$-value of only 0.00062 for the oxygen abundances, 
indicating only a 0.062\% chance that there will be a test statistic greater 
than 0.07 if the void sample is drawn from the wall sample.  The oxygen 
abundances for void galaxies are higher than the wall galaxies by an average of 
$0.04\pm 0.017$ in this absolute magnitude bin, reinforcing the results of the 
K-S test that there is a large-scale environmental influence on the oxygen 
abundance in galaxies with magnitudes $-19 > M_r > -20$.  While the results of 
the K-S test are not as convincing for this magnitude range in the nitrogen 
abundances, there is still an average shift of $0.02\pm 0.011$ toward higher 
nitrogen abundances for void galaxies.  While only one magnitude bin shows a 
statistically significant shift between the two environments, all magnitude bins 
are shifted in the same direction.  This trend suggests that there may be a mild 
influence on the chemical evolution of galaxies due to their large-scale 
environment.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_12logOH_stacked}
    \caption[Metallicity distribution of star-forming galaxies with 
    $-17 > M_r > -20$]{Gas-phase oxygen abundances relative to hydrogen of void 
    (red solid line) and wall (black dashed line) star-forming galaxies with 
    $-17 > M_r > -18$ (top), $-18 > M_r > -19$ (middle), and $-19 > M_r > -20$ 
    (bottom).  The results of a two-sample K-S test of the two data sets in each 
    absolute magnitude range can be found in Table \ref{tab:stats_P2}.  These 
    results are reflected visually, as there appears to be very little 
    difference between the two populations (regardless of absolute magnitude), 
    indicating that there is little large-scale environmental influence on the 
    oxygen abundance of star-forming galaxies with absolute magnitudes 
    $-17 > M_r > -20$.}
    \label{fig:Z_bright}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_12logNH_stacked}
    \caption[Nitrogen distribution of star-forming galaxies with 
    $-17 > M_r > -20$]{Abundance of nitrogen relative to hydrogen of void (red 
    solid line) and wall (black dashed line) star-forming galaxies with 
    $-17 > M_r > -18$ (top), $-18 > M_r > -19$ (middle), and $-19 > M_r > -20$ 
    (bottom).  The results of a two-sample K-S test of the two data sets in each 
    absolute magnitude range can be found in Table \ref{tab:stats_P2}.  These 
    results are reflected visually, as there appears to be very little 
    difference between the two populations (regardless of absolute magnitude), 
    indicating that there is little large-scale environmental influence on the 
    nitrogen abundance of star-forming galaxies with absolute magnitudes 
    $-17 > M_r > -20$.}
    \label{fig:N_bright}
\end{figure}

@@

%%%% Brighter star-forming galaxies %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We perform the same analysis with the N/O ratio on somewhat brighter galaxies, 
up through $M_r > -20$; the results of this analysis can be seen in Fig. 
\ref{fig:NO_bright} and in Table \ref{tab:stats_P2}.  The shift toward lower N/O 
ratios for the void galaxies is small for all magnitude bins.  The direction of 
the shift between environments for the N/O ratio is consistent for all absolute 
magnitude bins: void galaxies have slightly lower N/O ratios than wall galaxies.  
This is only very weak evidence of a large-scale environmental influence on the 
relative abundances of elements in galaxies, but it is worth testing for in 
larger samples.

% 17-18
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_logNO_stacked}
    \caption[N/O distribution of star-forming galaxies with $-17 > M_r > -20$]
    {Ratio of nitrogen to oxygen of void (red solid line) and wall (black dashed 
    line) star-forming galaxies with $-17 > M_r > -18$ (top), $-18 > M_r > -19$ 
    (middle), and $-19 > M_r > -20$ (bottom).  The results of a two-sample K-S 
    test of the two data sets in each absolute magnitude range can be found in 
    Table \ref{tab:stats_P2}, in addition to other statistics of the samples.  
    Both the histograms, CDFs, and statistics suggest a very slight difference 
    between the two populations, indicating a mild large-scale environmental 
    influence on the relative chemical abundances of star-forming galaxies with 
    absolute magnitudes $-17 > M_r > -20$.}
    \label{fig:NO_bright}
\end{figure}

@@

	\label{tab:stats_P2}

@@

The majority of the shifts in the gas-phase abundances of oxygen, nitrogen, and 
the N/O ratio seen in galaxies fainter than $L_*$ are small and statistically 
insignificant.  However, they occur in almost the same direction across all 
magnitude bins.  This trend suggests that the gas-phase abundances may be 
influenced by the galaxies' large-scale environments.  \cite{Shields91} find no 
offset in the N/O ratio between cluster and field galaxies, despite the 
difference in O/H they observe.  Similar to us, \cite{Contini02} and 
\cite{Pilyugin02} also find a statistically insignificant shift in the N/O ratio 
of cluster galaxies, although they find that these galaxies have lower N/O 
ratios than field spiral galaxies.  Based on Fig. \ref{fig:NOratio} and the 
statistics in Table \ref{tab:stats_P2}, we find weak evidence that void dwarf 
galaxies have a smaller N/O ratio than dwarf galaxies in denser regions.  This 
means that void dwarf galaxies may have more oxygen than wall dwarf galaxies, 
and/or void dwarf galaxies could have less nitrogen than wall dwarf galaxies.  
Here we discuss these possibilities and explore their implications for the 
large-scale environmental impact on the formation and evolution of galaxies.

@@

Table \ref{tab:stats_P2} suggests a slight large-scale environmental dependence 
of the oxygen and nitrogen abundances (relative to hydrogen), where void 
galaxies have slightly more O/H and N/H than wall galaxies.  This small 
difference is not apparent when looking at Figs. \ref{fig:met1sig} and 
\ref{fig:N_1sig}.  However, the N/O ratio amplifies this large-scale 
environmental effect so that a shift in the mean (or median) of the two 
populations can be seen in Fig. \ref{fig:NOratio}.  We hesitate to combine the 
results across all magnitude bins in an effort to improve their significance.  
Instead, we look toward the future to analyze a larger sample of galaxies to 
increase the statistical significance of these results.

@@

Applying the results of these simulations to our dwarf galaxy sample, if the 
ratio of dark matter halo mass to stellar mass is larger in void galaxies, the 
metals ejected from a void galaxy's ISM into its circumgalactic medium are more 
likely to fall back onto the ISM than in a wall galaxy with the same stellar 
mass, since the void galaxy's virial radius and potential well are larger.  As a 
result, two dwarf galaxies with the same stellar mass in these two different 
large-scale environments can have different metallicities --- void dwarf 
galaxies would have higher metallicities than wall dwarf galaxies, matching what 
we see in Table \ref{tab:stats_P2}.
